Inventor Disambiguation Report

### 2022-05-21 examples/benchmark/full-report.qmd
update

summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
```

@@

```{python}
summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
```

@@

```{python}
summarizer.get_top_inventors()
```

@@

```{python}
summarizer.plot_entropy_curve()
```

@@

```{python}
summarizer.plot_cluster_unique_name_distribution(range=(0, 100))
```

@@

```{python}
summarizer.plot_homonymy_rate_distribution()
```

@@

```{python}
inventor_benchmark_plot(disambiguations)
```

@@

```{python}
#| column: page
from pv_evaluation.benchmark import (
    load_israeli_inventors_benchmark,
    load_patentsview_inventors_benchmark,
    inspect_clusters_to_split,
    inspect_clusters_to_merge
)

inspect_clusters_to_split(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
```

@@

```{python}
#| column: page
inspect_clusters_to_split(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
```

@@

```{python}
#| column: page
inspect_clusters_to_merge(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
```

@@

```{python}
#| column: page
inspect_clusters_to_merge(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
```

>>>>

#summarizer = InventorDisambiguationSummary("rawinventor.tsv", processed_data_dir=".", name="current disambiguation")
```

@@

```{python}
#summarizer.plot_cluster_size_distribution(range=(0.5,10.5))
```

@@

```{python}
#summarizer.get_top_inventors()
```

@@

```{python}
#summarizer.plot_entropy_curve()
```

@@

```{python}
#summarizer.plot_cluster_unique_name_distribution(range=(0, 100))
```

@@

```{python}
#summarizer.plot_homonymy_rate_distribution()
```

@@

```{python}
#inventor_benchmark_plot(disambiguations)
```

@@

```{python}
from IPython.core.display import display, HTML

#| column: page
from pv_evaluation.benchmark import (
    load_israeli_inventors_benchmark,
    load_patentsview_inventors_benchmark,
    inspect_clusters_to_split,
    inspect_clusters_to_merge,
    style_cluster_inspection,
)

def style_and_display(table, by="prediction"):
    return display(HTML(style_cluster_inspection(table.reset_index(), by=by).hide_index().to_html()))

style_and_display(inspect_clusters_to_split(disambiguations["current"], load_israeli_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["current"], load_patentsview_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["current"], load_israeli_inventors_benchmark()), by="reference")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["current"], load_patentsview_inventors_benchmark()), by="reference")
```
